---
title: "BUSAD40 - Business Statistics"
subtitle: "Online Activity 3"
author: "Your Name"
date: "8/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1

Given the simulated normally distributed data. Answer the following questions with your code.

a. Plot a histogram to show the distribution of the simulated data.

b. Assign the mean of the data set to **m** and standard deviation to **sd**.

c. Find the probability for randomly select a score **below 30** from this simulated data. P(X<30)

d. Find the probability for randomly select a score **above 50** from this simulated data. P(X>50)

e. Find the probability for randomly select a score **between 30 and 50** from the simulated data. P(30<X<50)

f. What is the score that is at the **80th percentile** of this data? P(X < x) = 0.8

```{r}
# Simulate a normally distributed data set
n <- rnorm(5000, mean = 42, sd = 5)

# Enter your code here!
# Part a



# Part b



# Part c



# print(paste("The probabability to randomly select a score below 100 is ", ))

# Part d



# print(paste("The probabability to randomly select a score above 150 is ", ))

# Part e



# print(paste("The probabability to randomly select a score between 110 and 130 is ", ))

# Part f



# print(paste("The score that is at 90th percentile in the data set is ", ))

```