---
title: "BUSAD40 - Business Statistics"
subtitle: "Online Activity 4"
author: "Your Name"
date: "8/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1

Given the following information, calculate the related test statistic in each case. 

a. $\mu$ = 33, $\sigma$ = 4.55, $\bar{x}$ = 37, $s$ = 6.2, $n$ = 52

```{r}
# Enter your code here!



print(paste(""))
```

b. $\mu$ = 122, $\bar{x}$ = 108, $s$ = 15.3, $n$ = 82

```{r}
# Enter your code here!


print(paste(""))
```

c. Calculate the confident intervals in the following case.

$\mu$ = 76.4, $\sigma$ = 4.88, $\bar{x}$ = 81.7, $s$ = 8.2, $n$ = 103

```{r}
# Enter the code here!


print(paste(""))
```


d. Calculate the p value in the following case.

$\mu$ = 64.55, $\sigma$ = 7.82, $\bar{x}$ = 60.14, $s$ = 11.45, $n$ = 34

```{r}
# Enter the code here!


print(paste(""))
```

***

### Question 2

A market research surveyed 200 random residents in California about their willingness to pay for the mobile phone service. The mean from this survey is \$33.50 with standard deviation \$4.55. Given that the population mean is \$31.24. Answer the following questions,

a. Create the 95% confidence intervals to demonstrates the willingness to pay for the mobile phone service in California.

b. Create a null hypothesis ($\bar{x} = \mu$) and run the testing at significant level $\alpha$ = 0.05. Note: this is an two-tail test.

c. Make a conclusion about the test result.

```{r}
# Enter your code here!
# Part a


print(paste(""))
# Part b


print(paste(""))
# Part c


print(paste(""))
```