---
title: "BUSAD40 - Business Statistics"
author: "Your Name"
date: "8/24/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
    highlight: tango
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter Assignment 2

* Complete the following questions to earn full grade in this assignment.
* Some of the questions require students to show works to earn full credit.
* After finished the assignment, knit the Markdown file into HTML file for submission.

### Question 1

Given the probability of the following events and assume that they are independent, answer all the questions for full credit.

Event A: P(A) = 0.35 

Event B: P(B) = 0.44

Event C: P(C) = 0.12


1. What is the probability that Event A and Event B happen at the same time? $P(A \cap B)$

Ans: 

2. What is the probability either Event B or Event C happen? $P(B \cup C)$

Ans:

3. What is the probability Event B happen given Event A? $P(B|A)$

Ans:


### Question 2

Given the following situations, which of the probability distribution would be the most appropriate to apply?

|  Distribution List         |
|  :----------------------:  |
|  Normal Distribution       |
|  Exponential Distribution  |
|  Binomial Distribution     |
|  Poisson Distribution      |

1. As a quality control inspector, your job is to ensure the product quality meeting the company standard. Inspectors usually check the product from the production and count the number of inspected items until they find a defect. 

Ans: 

2. During a marathon race, the host organization usually track the finish time of all the runners and putting them into ranking. When aggregate all the players finish time together, we can construct a distribution for the race.

Ans:

3. A tech company is interested to figure out the behavior of their customers and how long they stay on their company web page. Given the ability to track the page visit time, the company can construct a distribution to describe the page visitor behavior.

Ans:

4. In the World Cup, an average of 2.5 goals are scored each game. Modeling this situation, we can use a distribution to approximate the probability that k goals are scored in a game.

Ans: 


### Question 3

The UCBAdmission data set is the aggregate data on applicants to graduate school at Berkeley for the six largest departments in 1973 classified by admission and sex.

Using the data set to answer the following questions: (Show Work!!)

```{r, include=FALSE}
library(vcd)
```
```{r, echo=FALSE}
# Aggregate the application data
data("UCBAdmissions")
univ <- apply(UCBAdmissions, c(1,2), sum)
univ

# Visualize the proportion
UCB <- aperm(UCBAdmissions, c(2, 1, 3))
fourfold(margin.table(UCB, c(1,2)))

# Admission by Department
fourfold(UCBAdmissions, mfrow=c(2,3))


# Frequency table by department
ftable(UCBAdmissions, c(2,3),
       row.vars="Dept", col.vars = c("Gender", "Admit"))

print(paste("The total number of applications: ", sum(UCBAdmissions)))
```

1. Suppose you are one of the administration staff who handle the applications. Based on this information, what is your probability that you randomly pick an application from a female applicant? $P(Gender=Female)$

Ans: 


2. What is the probability that you randomly pick an application for Department A? $P(Department=A)$

Ans: 


3. What is the probability that you randomly pick an application that got admitted? $P(Admitted=Yes)$

Ans: 


4. What is your probability a randomly picked application is from a male applicant and admitted by UCB? $P(Admitted=Yes \cap Gender=Male)$

Ans:


5. What is the probability a randomly picked application is a female applicant who is applying to department C? $P(Gender=Female \cap Department=C)$

Ans:


6. What is the probability a randomly picked application is applying either department B, D, or F? $P(Department=B \cup Department=D \cup Department=F)$

Ans:


7. What is the probability a randomly selected application is a female applicant who is applying to department A and successfully gets admitted? $P(Gender=Female \cap Department=A \cap Admitted=Yes)$

Ans:


8. What is the probability a randomly selected application is admitted by UCB given that the applicant is a female? $P(Admitted=Yes | Gender=Female)$

Ans:


### Question 4:

Suppose you are running a small local business.  You have a shipment just arrived from your supplier and below is the table of the summary about the quality of the shipment.

|  Category     |  Defect  |  Not Defect  |
|  :---------:  |  :----:  |  :--------:  |
|  Bag          |  5       |  83          |
|  Shoes        |  10      |  265         |
|  Socks        |  33      |  832         |
|  Accessories  |  18      |  628         |

Given the summary table, answer the following probability questions: (Show Work!!)

1. What is the probability for your customer randomly pick an item that is an accessory and not defect?

Ans:


2. What is the probability for your customer randomly pick an item that is a bag and defect?

Ans:  


3. What is the probability for your customer randomly pick a defected product given that is a pair of shoes?

Ans: 


### Question 5:

The record of shipping time from China to the U.S. approximates a normal distribution with mean of 31.3 days and standard deviation of 3.2 days. Answer the following questions with the information given: (Show Work!!)

1. What is the z score if a shipment arrived by the 34th day?

Ans:

2. What is the probability that a shipment arrived on or after 34th day?

Ans:

3. What length of time marks the shortest 75% of all shipment?

Ans:

4. What is the upper bound and lower bound length of time for a shipment arrive within 2 standard deviation from the mean?

Ans:


### Question 6:

Suppose you are given a task to test your company security system.  The probability the system passing the test is 95%. You are going run the test 5 times. what is the probability the system passes the test exactly 4 times? (Hint: use the binomial distribution function) (Show Work!!)

Ans:


### Question 7:

Use the standard normal distribution table to look up the answer for the following questions:  

1. What is the probability for P(Z < 1.5)?

Ans:

2. What is the probability for P(Z > 2.2)?

Ans:

3. What is the probability for P(-1.3 < Z < 1.3)

Ans:

4. What is the probability for P(-1.6 > Z > 1.6)

Ans:
