---
title: "BUSAD40 - Business Statistics"
author: "Your Name"
date: "8/24/2020"
output: 
  html_document:
    theme: united
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter Assignment 4

* Complete the following questions to earn full grade in this assignment.
* Some of the questions require students to show works to earn full credit.
* After finished the assignment, knit the Markdown file into HTML file for submission.

### Question 1

Given are five observations for two variable, x and y.

|   y   |   x   |
| :---: | :---: |
|   3   |   1   |
|   7   |   2   |
|   5   |   3   |
|   11  |   4   |
|   14  |   5   |

a. Calculate the mean for x and y. (Show Work!)


$\bar{x}$ = 


$\bar{y}$ = 


b. Calculate and fill out the rest of the statistics in the table.

| $x_i-\bar{x}$ | $y_i-\bar{y}$ | $(x_i-\bar{x})(y_i-\bar{y})$ | $(x_i-\bar{x})^2$ | 
|  :---:  |  :---:  |  :---:  |  :---:  |
|  **-2** | **-5**  |  **10** |  **4**  |
|         |         |         |         |
|         |         |         |         |
|         |         |         |         |
|         |         |         |         |


c. Calculate the covariance of x and y. Does your answer illustrate a positive or negative relationship between x and y? (Show Work!)

Ans: 


d. Calculate the correlation of x and y. Does your answer illustrate a strong or weak correlation between x and y? (Show Work!)

Ans: 


e. Calculate the estimated slope of the regression model. (Show Work!)

$\beta_1$ = 


f. Calculate the estimated y-intercept of the regression model. (Show Work!)

$\beta_0$ = 


g. Write out the estimated regression equation fitting the data. 

Ans:


h. Complete the following table:

| $\hat{y}_i$ | $(y_i-\hat{y}_i)^2$ | $(y_i-\bar{y})^2$ | $(\hat{y_i}-\bar{y})^2$ |
|  :---:  |  :---:  |  :---:  |  :---:  |
|         |         |         |         |
|         |         |         |         |
|         |         |         |         |
|         |         |         |         |
|         |         |         |         |


i. Calculate the Residual Sum of Squares, Total Sum of Squares, and Explained Sum of Squares with the results from part f.

Residual Sum of Squares = 

Total Sum of Squares = 

Explained Sum of Squares = 


***

### Question 2

Given the following summary output, answer each of the question in this problem:

```{r}
#Call:
#lm(formula = medv ~ lstat, data = Boston)

#Residuals:
#    Min      1Q  Median      3Q     Max 
#-15.168  -3.990  -1.318   2.034  24.500 

#Coefficients:
#            Estimate Std. Error t value Pr(>|t|)    
#(Intercept) 34.55384    0.56263   61.41   <2e-16 ***
#lstat       -0.95005    0.03873  -24.53   <2e-16 ***
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#Residual standard error: 6.216 on 504 degrees of freedom
#Multiple R-squared:  0.5441,	Adjusted R-squared:  0.5432 
#F-statistic: 601.6 on 1 and 504 DF,  p-value: < 2.2e-16
```
```{r, echo=FALSE}
library(MASS)
plot(medv ~ lstat, Boston, 
     main = "Housing Values in Suburbs of Boston",
     xlab = "Lower Status of the Population (Percent)",
     ylab = "Median Value of Owner-Occupied Homes in $1,000s")
fit1 <- lm(medv ~ lstat, data = Boston)
abline(fit1, col = "blue", lwd = 2)
```

a. According to the summary output, what is the marginal effect of lstat (lower status of the population) to the medv (median value of owner-occupied homes)?

Ans:

b. Calculate the t statistics for the estimated parameter for lstat, $\beta_1$. Show work!

Ans:

c. Interpret the p-value for the estimated parameter for lstat, $\beta_1$. 

Ans:

d. Interpret the $R^2$ of the model.  

Ans:

e. Interpret the p-value of the F test and make a conclusion about the overall significancy of the model.

