---
title: "BUSAD40 R Assignment 3"
author: "Your Name"
date: "8/24/2020"
output: 
  html_document:
    theme: united
    highlight: tango
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Assignment 3

* In this assignment, we are going to apply some of the build in data set in R for descriptive statistics analysis.
* To earn full grade in this assignment, students need to comlete the coding tasks for each questions to get the final result.
* After finished all the questions, knit the document into HTML format for submission.

### Question 1

Given the following information, calculate the z score in each case. 

a. $\mu$ = 46, $\sigma$ = 3.4, $\bar{x}$ = 40, $s$ = 5.6, $n$ = 58

```{r}
# Enter your code here!

```

b. $\mu$ = 154, $\sigma$ = 11.6, $\bar{x}$ = 164, $s$ = 22.4, $n$ = 120

```{r}
# Enter your code here!

```


### Qustion 2

Given the following information, calculate the t statistic in each case.

a. $\mu$ = 48.2, $\bar{x}$ = 50, $s$ = 8.3, $n$ = 33

```{r}
# Enter your code here!

```

b. $\mu$ = 86.2, $\bar{x}$ = 82.4, $s$ = 12.7, $n$ = 62

```{r}
# Enter your code here!

```

### Question 3

Calculate the confident intervals in each of the following case.

a. $\mu$ = 46, $\sigma$ = 3.4, $\bar{x}$ = 40, $s$ = 5.6, $n$ = 58, $\alpha$ = 0.05

```{r}
# Enter the code here!

```

b. $\mu$ = 48.2, $\bar{x}$ = 50, $s$ = 8.3, $n$ = 33, $\alpha$ = 0.01

```{r}
# Enter your code here!

```

### Question 4

Calculate the p value in each of the following case.

a. $\mu$ = 43.2, $\sigma$ = 12.4, $\bar{x}$ < 40, $s$ = 5.6, $n$ = 84, $\alpha$ = 0.10

```{r}
# Enter the code here!

```

b. $\mu$ = 48.2, $\bar{x}$ > 50, $s$ = 8.3, $n$ = 33, $/alpha$ = 0.05

```{r}
# Enter your code here!

```

### Question 5

In a tech company, a project manager is planning on running an online promotion, whcih offers a 50% discount pomotion code on their service for the first three months. The previous pomotion events shows the average revenue per account is \$488 with standard deviation \$52. Suppose the manager started with 100 existing accounts to send them the code. The average revenue returned from the 100 accounts is \$500 with standard deviation \$68.  Answer the following question based on the given information.

a. Create the 95% confidence intervals to demonstrates the potential return from the online promotion.

b. Create a null hypothesis ($\bar{x} \leq \mu$) and run the testing at significant level $\alpha$ = 0.01. Note: this is an one-sided test.

c. Make a conclusion about this test.

```{r}
# Enter your code here!
# Part a


# Part b


# Part c

```

#### Conclusion:

Ans: 


### Question 6

Suppose the US population average height is 64.68 inches and we would like to test if players in the WBA league is statistically higher than an average US citizen at 5% significant level. Given the WNBA data set, we have the record of the WNBA players and setup our hypothesis testing. Your task is to run the hypothesis test in R and write a conclusion statement based on the result of the test.

$H_o: \mu_{WNBA} \leq \mu_{US}$  
$H_a: \mu_{WNBA} > \mu_{US}$  
$\alpha = 0.05$

```{r, echo=FALSE}
# Import the data
wnba <- read.csv("data/wnba_data.csv")
head(wnba)
```
```{r}
# Enter your code here!

```

#### Conclusion:

Ans: 